Pre-/Post-Trikafta (Prospective)

### 2022-04-20 Christine Chan/Pre-post Trikafta Prospective/pre_post_trikafta_prospective_analysis.Rmd
correlations

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(cgmanalysis)
library(AGD)
library(pracma)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
}
knitr::opts_knit$set(root.dir = home_dir)
rm(home_dir)
```

@@

# Figures

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(cgmanalysis)
library(AGD)
library(pracma)
library(corrplot)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
}
knitr::opts_knit$set(root.dir = home_dir)
rm(home_dir)
```

@@

# Correlations

White text indicates the correlation coefficient $R$, and results are only shown for correlations significant at the p < 0.05 level.

```{r fig.width=10,fig.height=10}
change_df = df %>% group_by(Study.ID) %>% 
  summarise_at(vars(Weight..kg.,c.peptide.0.minute,`C Peptide Index`,
                    `Adapted Matsuda`,`C Peptide ODI`,iAUC_ratio,homa2B:homa2IR),
               .funs = diff) %>%
  rename("Change in Weight (kg)" = Weight..kg.,
         "Change in Fasting C-Peptide (pmol/L)" = c.peptide.0.minute,
         "Change in C Peptide Index" = `C Peptide Index`,
         "Change in Adapted Matsuda" = `Adapted Matsuda`,
         "Change in C Peptide ODI" = `C Peptide ODI`,
         "Change in C pep iAUC:Glucose iAUC" = iAUC_ratio,
         "Change in HOMA2 %B" = homa2B, "Change in HOMA2 %S" = homa2S,
         "Change in HOMA2 IR" = homa2IR)

M = cor(change_df[,2:ncol(change_df)])
testRes = cor.mtest(change_df[,2:ncol(change_df)])
corrplot(M, p.mat = testRes$p, method = 'circle', type = 'lower', insig='blank',
         addCoef.col ='white', number.cex = 0.8, order = 'AOE', diag=FALSE)
```

# Other Figures
